Figures

### 2019-05-02 figures/07_model-selection.Rmd
cleanup output

```{r ```{r 07_model_selection, fig.height=3, echo=FALSE}

@@

```{r brms_stan}
library(brms)
library(tidybayes)
library(modelr)

@@

get_variables(fit0)
plot(fit0, pars = "agvpct")

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- brm(formula = model_form, data = dt, 
           family = gaussian())

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- brm(formula = model_form2, data = dt, 
           family = gaussian())
---

@@

# plot prediction lines
# hu4_signif$ZoneID
hu4_id               <- hu4_signif$ZoneID[3]
conditions           <- data.frame(hu4vzoneid = hu4_id)
rownames(conditions) <- hu4_id

@@

plot(me_zone, ncol = 1)$agvpct + 
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[3]) + 
  ggtitle(hu4_id)

ggplot() + 
    geom_point(data = dplyr::filter(dt, 
                                  hu4vzoneid == hu4_id), 
             aes(x = agvpct, y = tp)) + 
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[3])

@@

----
# loo significance testing
loo0 <- loo(fit)
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)
loo_compare(loo0, loo1)

```

>>>>

```{r 07_model_selection, fig.height=3, echo=FALSE}

@@

```{r model_fitting, echo=FALSE}
library(brms)
library(tidybayes)
library(modelr)

@@

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- get_if_not_exists(brm_fit, "fit.rds", formula = model_form, data = dt)

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- get_if_not_exists(brm_fit, "fit1.rds", formula = model_form, data = dt)

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- get_if_not_exists(brm_fit, "fit2.rds", formula = model_form2, data = dt)
```

```{r model_diagnostics, echo=FALSE}
# get_variables(fit0)
plot(fit0, pars = "agvpct")

@@

# plot prediction lines
# hu4_signif$ZoneID
hu4_id               <- hu4_signif$ZoneID[2]
conditions           <- data.frame(hu4vzoneid = hu4_id)
rownames(conditions) <- hu4_id

@@

# plot(me_zone, ncol = 1)$agvpct # + 
  # geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
  #               broom::tidy(fit)$estimate[3]) + 
  # ggtitle(hu4_id)

# ggplot() + 
#     geom_point(data = dplyr::filter(dt, 
#                                   hu4vzoneid == hu4_id), 
#              aes(x = agvpct, y = tp)) + 
#   geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
#                 broom::tidy(fit)$estimate[3]) +
#   ylim(0, 450) + xlim(40, 90) + ggtitle(hu4_id)

@@

# loo significance testing
loo0 <- loo(fit)
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo0, loo1)
loo_compare(loo1, loo2)
```
